---
title: "Distance sampling approach for aerial survey data"
author: "Leonard Hambrecht"
date: "2024"
output: html_document
---

# Introduction

This script is imports aerial survey data and some vegetation layers.
Through a distance sampling approach, the detection curve is caluclated based on various vegetation variables and the best model is selected. Based on the best model, a density surface is calucated.
This approach is based on the example provided by David L. Miller [here](https://distancesampling.org/R/vignettes/mexico-analysis.html)

# Preamble
### Load packages
Load necessary libraries for analysis and visualization
```{r}
library(dsm)
library(ggplot2)
library(terra)
library(Distance)
library(sf)
library(dplyr)
library(tidyr)
library(units)
library(purrr)
library(dsims)
```

### Set variables
Set size of grid cells in metre
```{r}
GRID_SIZE <- 500
```

### Define functions

```{r}
# Function to load and transform spatial data
load_spatial_data <- function(moose_path, transects_path, sbfi_path, wmu_path, crs) {
  moose <- sf::st_read(moose_path) %>%
    sf::st_transform(crs = crs) %>%
    select(Latitude, Longitude, date, name)

  transects <- sf::st_read(transects_path, layer = "tracks") %>%
    sf::st_transform(crs = crs) %>%
    select(1)

  sbfi <- sf::st_read(sbfi_path) %>%
    sf::st_transform(crs = crs)

  wmu <- sf::st_read(wmu_path) %>%
    sf::st_transform(crs = crs)

  list(moose = moose, transects = transects, sbfi = sbfi, wmu = wmu)
}


# Function to split transects into segments
split_into_segments <- function(linestring) {
  total_length <- st_length(linestring)
  total_length <- if (!inherits(total_length, "units")) set_units(total_length, "m") else total_length
  stopifnot(as.numeric(total_length) > 0)

  total_length_km <- set_units(total_length, "km")
  num_segments <- ceiling(as.numeric(total_length_km))
  stopifnot(num_segments > 0)

  equal_segment_length <- total_length_km / num_segments
  segment_lengths <- rep(equal_segment_length, num_segments)
  segment_lengths[num_segments] <- total_length_km - sum(segment_lengths[1:(num_segments - 1)])

  points <- sf::st_line_sample(linestring, sample = seq(0, 1, length.out = num_segments + 1)) %>%
    st_cast("POINT")
  stopifnot(length(points) >= 2)

  segments <- map2(points[-length(points)], points[-1], ~ {
    segment <- st_sfc(st_linestring(x = st_coordinates(c(.x, .y))), crs = st_crs(linestring))
    st_sf(geometry = segment)
  })

  segments_sf <- do.call(rbind, segments)
  stopifnot(nrow(segments_sf) >= 1)

  segments_sf
}

# Function to create plot objects for predictions
grid_plot_obj <- function(fill, name, sf_obj) {
  data <- data.frame(fill = fill)
  names(data) <- name
  combined_sf <- sf_obj %>%
    mutate(id = row_number()) %>%
    left_join(data, by = c("id" = "row.names"))

  ggplot(combined_sf) +
    geom_sf(aes_string(fill = name)) +
    theme_minimal()
}
```

## The data
Import data
```{r}
data_paths <- list(
  moose_path = "D:\\WMU\\survey_data\\501_moose_locations.shp",
  transects_path = "D:\\WMU\\survey_data\\WMU 501 (2018-2019)\\WMU501_transects_2018.gpx",
  sbfi_path = "D:\\WMU\\base_data\\CA_Forest_Satellite_Based_Inventory_2020\\clipped\\sbfi_501.shp",
  wmu_path = "D:\\WMU\\base_data\\WMU\\wmu_501_3400.shp"
)
data <- load_spatial_data(data_paths$moose_path, data_paths$transects_path, data_paths$sbfi_path, data_paths$wmu_path, crs = 3400)
moose <- data$moose
transects <- data$transects
sbfi <- data$sbfi
wmu <- data$wmu
```

### Format data
```{r}
# Rename columns in sbfi
org_sbfi_names <- colnames(sbfi)
colnames(sbfi) <- c(
  # Basic information
  "OBJECTID", "ID", "TILE", "AREA_HA", "PERIMETER_M", "JURISDICTION", 
  "ECOZONE", "ECOPROVINCE", "ECOREGION", "MANAGEMENT",

  # Land Cover
  "LC_WATER", "LC_SNOW_ICE", "LC_ROCK_RUBBLE", "LC_EXPOSED_BARREN", 
  "LC_BRYOIDS", "LC_SHRUBS", "LC_WETLAND", "LC_WETLAND_TREED", 
  "LC_HERBS", "LC_CONIFEROUS", "LC_BROADLEAF", "LC_MIXEDWOOD", 
  "LC_TREED", "LC_FAO_FOREST", "LC_WETLAND_VEGETATION",

  # Disturbance by Fire
  "DISTURB_FIRE_PERC", "DISTURB_FIRE_YEAR", "DISTURB_FIRE_MAGNITUDE_MIN", 
  "DISTURB_FIRE_MAGNITUDE_MAX", "DISTURB_FIRE_MAGNITUDE_AVG", 
  "DISTURB_FIRE_MAGNITUDE_SD", "DISTURB_FIRE_MAGNITUDE_MEDIAN",

  # Disturbance by Harvest
  "DISTURB_HARVEST_PERC", "DISTURB_HARVEST_YEAR",

  # Recovery from Disturbance by Fire
  "RECOVERY_FIRE_MIN", "RECOVERY_FIRE_MAX", "RECOVERY_FIRE_AVG", 
  "RECOVERY_FIRE_SD", "RECOVERY_FIRE_MEDIAN",

  # Recovery from Disturbance by Harvest
  "RECOVERY_HARVEST_MIN", "RECOVERY_HARVEST_MAX", "RECOVERY_HARVEST_AVG", 
  "RECOVERY_HARVEST_SD", "RECOVERY_HARVEST_MEDIAN",

  # Age of the Forest
  "AGE_MIN", "AGE_MAX", "AGE_AVG", "AGE_SD", "AGE_MEDIAN", 
  "AGE_0_10", "AGE_10_20", "AGE_20_30", "AGE_30_40", "AGE_40_50", 
  "AGE_50_60", "AGE_60_70", "AGE_70_80", "AGE_80_90", "AGE_90_100", 
  "AGE_100_110", "AGE_110_120", "AGE_120_130", "AGE_130_140", 
  "AGE_140_150", "AGE_GT_150",

  # Canopy Structure
  "STRUCTURE_CANOPY_HEIGHT_MIN", "STRUCTURE_CANOPY_HEIGHT_MAX", 
  "STRUCTURE_CANOPY_HEIGHT_AVG", "STRUCTURE_CANOPY_HEIGHT_SD", 
  "STRUCTURE_CANOPY_HEIGHT_MEDIAN", "STRUCTURE_CANOPY_COVER_MIN", 
  "STRUCTURE_CANOPY_COVER_MAX", "STRUCTURE_CANOPY_COVER_AVG", 
  "STRUCTURE_CANOPY_COVER_SD", "STRUCTURE_CANOPY_COVER_MEDIAN",

  # Lorey's Height
  "STRUCTURE_LOREYS_HEIGHT_MIN", "STRUCTURE_LOREYS_HEIGHT_MAX", 
  "STRUCTURE_LOREYS_HEIGHT_AVG", "STRUCTURE_LOREYS_HEIGHT_SD", 
  "STRUCTURE_LOREYS_HEIGHT_MEDIAN",

  # Basal Area
  "STRUCTURE_BASAL_AREA_MIN", "STRUCTURE_BASAL_AREA_MAX", 
  "STRUCTURE_BASAL_AREA_AVG", "STRUCTURE_BASAL_AREA_SD", 
  "STRUCTURE_BASAL_AREA_MEDIAN", "STRUCTURE_BASAL_AREA_TOTAL",

  # Above-Ground Biomass (AGB)
  "STRUCTURE_AGB_MIN", "STRUCTURE_AGB_MAX", "STRUCTURE_AGB_AVG", 
  "STRUCTURE_AGB_SD", "STRUCTURE_AGB_MEDIAN", "STRUCTURE_AGB_TOTAL",

  # Tree Volume
  "STRUCTURE_VOLUME_MIN", "STRUCTURE_VOLUME_MAX", "STRUCTURE_VOLUME_AVG", 
  "STRUCTURE_VOLUME_SD", "STRUCTURE_VOLUME_MEDIAN", "STRUCTURE_VOLUME_TOTAL",

  # Species Composition
  "SPECIES_NUMBER", "SPECIES_1", "SPECIES_1_PERC", "SPECIES_2", 
  "SPECIES_2_PERC", "SPECIES_3", "SPECIES_3_PERC", "SPECIES_4", 
  "SPECIES_4_PERC", "SPECIES_5", "SPECIES_5_PERC", "SPECIES_CONIFEROUS_PERC", 
  "SPECIES_CML_1", "SPECIES_CML_1_PERC", "SPECIES_CML_2", 
  "SPECIES_CML_2_PERC", "SPECIES_CML_3", "SPECIES_CML_3_PERC", 
  "SPECIES_CML_4", "SPECIES_CML_4_PERC", "SPECIES_CML_5", 
  "SPECIES_CML_5_PERC", "SPECIES_CML_CONIFEROUS_PERC", 
  "SPECIES_CML_ASSEMBLAGES", "SPECIES_CML_ASSEMBLAGES_PERC",

  # Symbolic Levels and Others
  "SYMB_LAND_BASE_LEVEL", "SYMB_LAND_COVER_LEVEL", "SYMB_VEGETATION_LEVEL", 
  "SYMB_DISTURBANCE", "SYMB_RECOVERY", "SYMB_AGE", "Shape_Length", 
  "Shape_Area", "layer", "path", "geometry"
)

# Select only the OBJECTID column
wmu <- wmu[, "OBJECTID"]

# Perform spatial join to get the polygon attributes for each point
joined <- st_join(moose, sbfi)
result <- joined[, c("STRUCTURE_CANOPY_HEIGHT_MEDIAN", "STRUCTURE_CANOPY_COVER_MEDIAN", "STRUCTURE_AGB_MEDIAN", "STRUCTURE_AGB_TOTAL", "STRUCTURE_VOLUME_MEDIAN", "STRUCTURE_VOLUME_TOTAL")]

# Replace NA values with 0
result <- result %>% replace_na(list(STRUCTURE_CANOPY_HEIGHT_MEDIAN = 0, STRUCTURE_CANOPY_COVER_MEDIAN = 0, STRUCTURE_AGB_MEDIAN = 0, STRUCTURE_AGB_TOTAL = 0 , STRUCTURE_VOLUME_MEDIAN = 0, STRUCTURE_VOLUME_TOTAL = 0))

# Add the results to the original points sf object
moose$canopy_height <- round(result$STRUCTURE_CANOPY_HEIGHT_MEDIAN,0) # round values to group similar values together and speed up the computation of the detection function
moose$canopy_cover <- round(result$STRUCTURE_CANOPY_COVER_MEDIAN,0)
moose$agb <- round(result$STRUCTURE_AGB_MEDIAN,-1)
moose$agb_total <- round(result$STRUCTURE_AGB_TOTAL,-2)
moose$vol <- round(result$STRUCTURE_VOLUME_MEDIAN,-1)
moose$vol_total <- round(result$STRUCTURE_VOLUME_TOTAL,-2)

# Split transects into segments
transects_segments <- transects %>%
  st_cast("LINESTRING") %>%
  st_geometry() %>%
  map(split_into_segments) %>%
  bind_rows() %>%
  st_sf()

st_crs(transects_segments) <- st_crs(transects)
transects_segments$Sample.Label <- row_number(transects_segments)

# Calculate distances between moose points and transect segments
distances <- st_distance(moose, transects_segments, tolerance = set_units(600, "m"))

# Find closest segment for each moose point
closest_segments <- data.frame(
  moose_id = integer(nrow(moose)),
  Sample.Label = integer(nrow(moose)),
  distance = numeric(nrow(moose))
)

for (i in 1:nrow(moose)) {
  min_distance_index <- which.min(distances[i, ])
  closest_segments$moose_id[i] <- i
  closest_segments$Sample.Label[i] <- transects_segments$Sample.Label[min_distance_index]
  closest_segments$distance[i] <- distances[i, min_distance_index]
}

# Merge closest segments with moose data
moose <- merge(moose, closest_segments, by.x = "row.names", by.y = "moose_id")
colnames(moose)[1] <- "object"
colnames(moose)[5] <- "Transect.Label"
moose$size <- 1
moose$Effort <- 10
moose$distance <- moose$distance / 1000

# Prepare data for density surface modelling
segdata <- as.data.frame(sf::st_drop_geometry(moose[, c("Latitude", "Longitude", "Effort", "Transect.Label", "Sample.Label", "canopy_height", "canopy_cover", "agb", "agb_total", "vol", "vol_total")]))
distdata <- as.data.frame(sf::st_drop_geometry(moose[, c("object", "Latitude", "Longitude", "distance", "Effort", "size", "canopy_height", "canopy_cover", "agb", "agb_total", "vol", "vol_total")]))
distdata$detected <- 1
segdata$x <- distdata$x <- sf::st_coordinates(moose)[, 1]
segdata$y <- distdata$y <- sf::st_coordinates(moose)[, 2]
obsdata <- as.data.frame(sf::st_drop_geometry(moose[, c("object", "distance", "Effort", "Sample.Label", "size")]))
```

## Density surface template
Create simgple density object to retrieve coordinates from and fill later with predicted abundance values
```{r}
# Create the survey region
region <- make.region(
  region.name = "study area",
  shape = wmu
)
plot(region)

## # Create the density surface
density <- dsims::make.density(
  region = region,
  x.space = GRID_SIZE
)
coords <- sf::st_drop_geometry(density@density.surface[[1]][, c("x", "y")])
```

## Exploratory data analysis
Segmentation data
```{r}
head(segdata)
```

Observation data
```{r}
head(obsdata)
```
### Distance data
Data frame
```{r}
head(distdata)
```
Histogram
```{r}
hist(distdata$distance,main="",xlab="Distance (m)")
```
### Spatial data
Canopy height
```{r}
p <- ggplot() + grid_plot_obj(distdata$canopy_height, "Height", coords) + coord_equal()
p <- p + labs(fill="Height",x="x",y="y",size="Distance")
p <- p + geom_line(aes(x, y, group=Transect.Label), data=segdata)
p <- p + geom_point(aes(x, y, size=distance), data=distdata, colour="red",alpha=I(0.7))
p <- p + gg.opts
print(p)
```


# Estimating the detection function
The summary gives us information about parameter estimates, probability of detection, AIC. The plots show the fitted detection function and quantile-quantile plot.
Left: Fitted detection function
Right: Goodness of fit for the hazard-rate model

Null model
```{r}
detfc.hr.null <- ds(distdata, max(distdata$distance), key = "hr", adjustment = NULL)
summary(detfc.hr.null)
par(mfrow = c(1, 2))
plot(detfc.hr.null, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.null$ddf)
```

Adding covariates in the detection function is common. The AIC should idealy be lower then the null model and goodnes of fit should be better
Canopy height model
```{r}
detfc.hr.height <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(canopy_height),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.height)
plot(detfc.hr.height, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.height$ddf)
```

Canopy cover model
```{r}
detfc.hr.cover <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(canopy_cover),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.cover)
plot(detfc.hr.cover, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.cover$ddf)
```

AGB model
```{r}
detfc.hr.agb <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(agb),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.agb)
plot(detfc.hr.agb, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.agb$ddf)
```

AGB total model
```{r}
detfc.hr.agb_total <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(agb_total),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.agb_total)
plot(detfc.hr.agb_total, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.agb_total$ddf)
```

Volume model
```{r}
detfc.hr.vol <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(vol),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.vol)
plot(detfc.hr.vol, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.vol$ddf)
```

Volume total model
```{r}
detfc.hr.vol_total <- ds(distdata, max(distdata$distance),
  formula = ~ as.factor(vol_total),
  key = "hr", adjustment = NULL
)
summary(detfc.hr.vol_total)
plot(detfc.hr.vol_total, showpoints = FALSE, pl.den = 0, lwd = 2)
ddf.gof(detfc.hr.vol_total$ddf)

par(mfrow = c(1, 1))
```

# Fit a DSM
Fitting a simple model. The summary gives use the deviance explained which can be used to compare between models. Furthermore, the model can be plotted the show the spatial distrubution of the density.

Null model
```{r}
dsm.xy <- dsm(count ~ s(x, y), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy)
plot(dsm.xy, select = 2)
vis.gam(dsm.xy, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Canopy height
```
dsm.xy.height <- dsm(count ~ s(x, y, k = 10) + s(canopy_height, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.height)
plot(dsm.xy.height, select = 2)
vis.gam(dsm.xy.height, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Canopy cover
```{r}
dsm.xy.cover <- dsm(count ~ s(x, y, k = 10) + s(canopy_cover, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.cover)
plot(dsm.xy.cover, select = 2)
vis.gam(dsm.xy.cover, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
AGB
```{r}
dsm.xy.agb <- dsm(count ~ s(x, y, k = 10) + s(agb, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.agb)
plot(dsm.xy.agb, select = 2)
vis.gam(dsm.xy.agb, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
AGB total
```{r}
dsm.xy.agb_total <- dsm(count ~ s(x, y, k = 10) + s(agb_total, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.agb_total)
plot(dsm.xy.agb_total, select = 2)
vis.gam(dsm.xy.agb_total, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Volumne
```{r}
dsm.xy.vol <- dsm(count ~ s(x, y, k = 10) + s(vol, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.vol)
plot(dsm.xy.vol, select = 2)
vis.gam(dsm.xy.vol, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Volume total
```{r}
dsm.xy.vol_total <- dsm(count ~ s(x, y, k = 10) + s(vol_total, k = 20), detfc.hr.null, segdata, obsdata, method = "REML")
summary(dsm.xy.vol_total)
plot(dsm.xy.vol_total, select = 2)
vis.gam(dsm.xy.vol_total, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```

# Spatial models when there are covariates in the detection function
Canopy height
```{r}
dsm.est.xy_height <- dsm(abundance.est ~ s(x, y), detfc.hr.height, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_height, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Canopy cover
```{r}
dsm.est.xy_cover <- dsm(abundance.est ~ s(x, y), detfc.hr.cover, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_cover, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
AGB
```{r}
dsm.est.xy_agb <- dsm(abundance.est ~ s(x, y), detfc.hr.agb, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_agb, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
AGB total
```{r}
dsm.est.xy_agb_total <- dsm(abundance.est ~ s(x, y), detfc.hr.agb_total, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_agb_total, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Volume
```{r}
dsm.est.xy_vol <- dsm(abundance.est ~ s(x, y), detfc.hr.vol, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_vol, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```
Volume total
```{r}
dsm.est.xy_vol_total <- dsm(abundance.est ~ s(x, y), detfc.hr.vol_total, segdata, obsdata, method = "REML")
vis.gam(dsm.est.xy_vol_total, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```

Tweedie
```{r}
dsm.xy.tweedie <- dsm(count ~ s(x, y), detfc.hr.null, segdata, obsdata, family = tw(), method = "REML")
summary(dsm.xy.tweedie)
vis.gam(dsm.xy.tweedie, plot.type = "contour", view = c("x", "y"), asp = 1, type = "response", contour.col = "black", n.grid = GRID_SIZE)
```

# Model checking
Checking goodness of fit
The Q-Q plot should show a straight line for good fit
```{r}
gam.check(dsm.xy)
gam.check(dsm.xy.height)
gam.check(dsm.xy.cover)
gam.check(dsm.xy_agb)
gam.check(dsm.xy_agb_total)
gam.check(dsm.xy_vol)
gam.check(dsm.xy_vol_total)
gam.check(dsm.est.xy_height)
gam.check(dsm.est.xy_cover)
gam.check(dsm.est.xy_agb)
gam.check(dsm.est.xy_agb_total)
gam.check(dsm.est.xy_vol)
gam.check(dsm.est.xy_vol_total)
```

Randomised quantile residuals
same as `gam.check` but removes the 0's in the data which can cause distracting artefacts in the plots such as lines.
```{r}
rqgam_check(dsm.xy.tweedie)
```
Check for autocorrelation

```{r}
dsm_cor(dsm.xy, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy.height, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy.cover, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy_agb, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy_agb_total, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy_vol, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.xy_vol_total, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_height, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_cover, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_agb, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_agb_total, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_vol, max.lag = 10, Segment.Label = "Sample.Label")
dsm_cor(dsm.est.xy_vol_total, max.lag = 10, Segment.Label = "Sample.Label")
```

# Model selection
make a data.frame to print out
```{r}
mod_results <- data.frame(
  "Model name" = c(
    "`dsm.xy`", "`dsm.xy.tweedie`", "`dsm.xy.height`", "`dsm.xy.cover`", "`dsm.xy_agb`", "`dsm.xy_agb_total`", "`dsm.xy_vol`", "`dsm.xy_vol_total`",
    "`dsm.est.xy_height`", "`dsm.est.xy_cover`", "`dsm.est.xy_agb`", "`dsm.est.xy_agb_total`", "`dsm.est.xy_vol`",
    "`dsm.est.xy_vol_total`"
  ),
  "Description" = c(
    "Bivariate smooth of location, quasipoisson",
    "Bivariate smooth of location, Tweedie, quasipoisson",
    "Bivariate smooth of location, smooth of height, quasipoisson",
    "Bivariate smooth of location, smooth of cover, quasipoisson",
    "Bivariate smooth of location, smooth of AGB, quasipoisson",
    "Bivariate smooth of location, smooth of AGB total, quasipoisson",
    "Bivariate smooth of location, smooth of Volume, quasipoisson",
    "Bivariate smooth of location, smooth of Volume total, quasipoisson",
    "Bivariate smooth of location, Tweedie, height covariate in detection function",
    "Bivariate smooth of location, Tweedie, cover covariate in detection function",
    "Bivariate smooth of location, Tweedie, AGB covariate in detection function",
    "Bivariate smooth of location, Tweedie, AGB total covariate in detection function",
    "Bivariate smooth of location, Tweedie, Volume covariate in detection function",
    "Bivariate smooth of location, Tweedie, Volume total covariate in detection function"
  ),
  "Deviance explained" = c(unlist(lapply(
    list(
      dsm.xy,
      dsm.xy.tweedie,
      dsm.xy.height,
      dsm.xy.cover,
      dsm.xy_agb,
      dsm.xy_agb_total,
      dsm.xy_vol,
      dsm.xy_vol_total
      dsm.est.xy_height,
      dsm.est.xy_cover,
      dsm.est.xy_agb,
      dsm.est.xy_agb_total,
      dsm.est.xy_vol,
      dsm.est.xy_vol_total
    ),
    function(x) {
      paste0(round(summary(x)$dev.expl * 100, 2), "%")
    }
  )))
)

library(knitr)
kable(mod_results, col.names = c("Model name", "Description", "Deviance explained"))
```

# Abundance estimation
```{r}
dsm.xy.pred <- predict(dsm.xy, coords, dsm.xy$offset[1])
# Calculate total abundance over the survey area
sum(dsm.xy.pred)

# fill density object with predeicted values
density@density.surface[[1]]$density <- dsm.xy.pred

# plot density
plot(density)
```
